VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-29 snapshot_system/paper_del.tex
rv

Snapshot deletions can occur frequently since old snapshots become less useful.
General deduplication complicates the deletion process because sharing of duplicates
requires a global refence counting to identify if  a chunk can be  safely removed without any reference.
%The complexity of our distributed environment obviates reference counting as an option,
%and While we can use the mark-and-sweep, 
%While the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
%it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
%
%In the case of Alibaba, snapshot backup is conducted automatically and there are 
%about 10 snapshot stored for every VM customer.
% Snapshot deletion can occur frequently, for example when there is
% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
% balanced storage use. 
%In addition, cloud users expect the reduced storage usage to be reflected
%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
Since our VM-centric design restricts sharing of data chunks only to a small dataset,
we can greatly simplify the deletion process by 
focusing on  unreferenced non-PDS chunks within each VM. 
This process can be conducted by independent among VMs, and thus results in  a simpler flow control and 
lower resource usage. 
%The PDS data chunks are commonly shared among all VMs and we do not consider them
%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.

>>>>

Snapshot deletions can occur frequently since old snapshots become less useful.
General deduplication complicates the deletion process because sharing of duplicates
requires a global refence counting~\cite{Guo2011,Fabiano2013} 
 to identify if  a chunk can be  safely removed without any reference.
%The complexity of our distributed environment obviates reference counting as an option,
%and While we can use the mark-and-sweep, 
%While the mark-and-sweep techniques can be used and optimization can be considered~\cite{Fabiano2013},
%it still takes significant resources to conduct reference counting every time there is a snapshot deletion.
%
%In the case of Alibaba, snapshot backup is conducted automatically and there are 
%about 10 snapshot stored for every VM customer.
% Snapshot deletion can occur frequently, for example when there is
% a new snapshot created every day,  there will usually be a snapshot expired every day to maintain
% balanced storage use. 
%In addition, cloud users expect the reduced storage usage to be reflected
%instantly, which makes it difficult to adopt some resource efficient techniques such like perfect hashing\cite{Fabiano2013}.
Since our VM-centric design restricts sharing of data chunks only to a small dataset,
we can greatly simplify the deletion process by 
focusing on  unreferenced non-PDS chunks within each VM. 
This process can be conducted by independent among VMs, and thus results in  a simpler flow control and 
lower resource usage. 
%The PDS data chunks are commonly shared among all VMs and we do not consider them
%during snapshot deletion.  The selection of PDS data chunks is updated periodically independent of snapshot deletion process.
